Strings functions analysis

### 2022-08-19 article.tex
another class function problem simplified

    It is worth noting that functions which have had this problem are popular (note here that we mean functions for all classes, not specifically string functions), this we have obtained by making queries about the number of times they occur for code bases. For this reason, this data will not be counted in this article, but a function for solving this problem is given in the Discussion section.

>>>>

    It is worth noting that functions which have had this problem are popular, this we have obtained by making queries about the number of times they occur for code bases. For this reason, this data will not be counted in this article.
